Correcting K-correction: dark energy is based on a math error from 1930

### 2025-01-09 paper/dark_energy_corrections.tex
Edits

\begin{abstract}
We rederive the K-correction equation and discover that the version of the
equation that is commonly used to calculate magnitudes contains three errors.
The oldest of these errors traces back nine decades; in 1930 the equation did
not correct for spectral bandwidth stretching, followed by a rederivation in
1968 that accounted for spectral bandwidth stretching but did not correct for
time dilation. Two new errors were introduced in 1996, one of which causes
systematic distance biases by inverting the zero-point correction term. We
conclude that properly correcting apparent magnitudes for redshift resolves two
of the preeminent mysteries in cosmology: first, dark energy is not supported
by observations of Type Ia supernovae and second, the Hubble tension is due to
the errors in the K-correction equation.
\end{abstract}

@@

The effect of using an incorrect magnitude for SnIa is that we think objects
are farther away than they really are, and the effect compounds for greater
distances. Up until \citet{riess1998}, we did not have distant enough
observations for this error to matter much for cosmological models, but by the
late 1990s, it became clear that our measurements for distance and redshift were
not linear. This realization led to a model that utilized a cosmological
constant $\Lambda$ and dark energy in order to explain the non-linear
distance-redshift graph. We will show in Section \ref{sec:conclusions} that
correcting the flaws with K-correction leads to a linear graph that does not
need to rely on a cosmological constant.

@@

Observational data from SnIa are essential for the calibration of models that
use redshift to estimate distance. The approximately linear relationship
between redshift and luminosity distance, often called the Hubble-Lema\^{i}tre law,
describes how quickly the universe is expanding. However, \citet{riess1998}
and \citet{perlmutter1999} presented evidence that there isn't a linear
relationship between redshift and distance, but instead, distant objects are
farther away than their redshift would predict (see Figure
\ref{fig:mu_distance_vs_redshift}). This phenomenon implies that the
acceleration of the universe is faster today than it was for old observations.
Previously the cause of this phenomenon was unknown and was referred to as dark
energy.

\begin{figure}
  \plotone{lum_distance_vs_redshift.pdf}
  \caption{The relationship between luminosity distance and redshift for two
  treatments of magnitude data. The displayed points are roughly a third of the
  values in the full SnIa dataset published in \citet{abbott2024}, selected
  evenly to aid visibility. The red $k(z) = 1$ treatment, which represents the
  uncorrected values, is clearly non-linear while the blue $k(z) = 1 + z$
  treatment, which fixes the K-correction redshift error, appears to be linear.}
  \label{fig:mu_distance_vs_redshift}
\end{figure}

@@

\begin{figure}
  \plotone{k_equation_flow.pdf}
  \caption{The ratio $K'_{xy}$ is the crux of the K-correction algorithm. We
  are able to observe a SnIa in the redshifted observation frame, but we want
  to compute the magnitude in the rest frame as if no redshift has occurred.
  This computation starts with $F(\lambda$, the spectral energy density, which
  we then convert to $F'(\lambda)$, the photon density for the rest frame. We
  show the process of computing $R'(\lambda$, the photon density in the
  observation frame, in three phases starting at the top right of the figure.
  First we stretch the photon density, but this step inflates counts. In the
  second step, we correct for the inflated counts by multiplying by $1/(1+z)$;
  at this point, the total count equals the total count of $F'(\lambda)$.
  Finally, in the third step we finish calculating the observation frame photon
  density $R'(\lambda)$ by accounting for time dilation, which also reduces
  photon counts by a factor of $1/(1+z)$. We can compute the expected ratio of
  photons by totalling the area under the curves in the bottom two panels. This
  example does not show the process of converting photon flux to magnitude, nor
  does it address the zero-point correction.
  }
  \label{fig:k-example}
\end{figure}

@@

  In order to account for this spectral bandwidth stretching effect, we will need
  to multiply $F'$ by a second factor of $1/(1+z)$.
  \item The stretching of space increases the distance between photons while
  they are traveling. This phenomenon appears to an observer like time
  dilation, although cosmological time dilation is due to a different mechanism
  than relativistic time dilation. This effect reduces the photon arrival rate
  by a factor of $1/(1+z)$.

  In order to account for cosmological time dilation, we will need to multiply
  $F'$ by $1/(1+z)$.
\end{itemize}

@@

In order to calculate the amount of flux $\mathcal{F}_x$ measured in filter
$x$, we need to compute the photon density $F'(\lambda)$ and multiply it by
sensitivity $S_x(\lambda)$, which represents the proportion of photons filter $x$
will measure at wavelength $\lambda$. We then need to sum over all wavelengths,
which is expressed with the equation

@@

\noindent The limits of integration are technically from 0 to $\infty$, but these are
usually not written because the sensitivity $S(\lambda)$ is 0 for wavelengths
outside of a filter's bandpass.

@@

\section{Conclusions}
\label{sec:conslusions}

\begin{figure}
  \plotone{velocity_vs_distance.pdf}
  \caption{The relationship between expansion velocity and distance. The slope
  of this graph demonstrates the Hubble constant. The data for these SnIa
  observations comes from the Dark Energy Spectroscopic Instrument
  \citep{vincenzi2024}, but the magnitudes are corrected to account for time
  dilation by adding $-2.5 log(1 + z)$.
  }
\label{fig:expansion}
\end{figure}

>>>>

\begin{abstract}
We rederive the K-correction equation and discover that the version commonly
used to calculate magnitudes contains three errors, and the oldest of these errors
traces back nine decades. The 1930 the equation did not correct for spectral
bandwidth stretching. Two new errors were introduced in 1996, one of which
causes systematic distance biases by inverting the zero-point correction term.
We conclude that properly correcting apparent magnitudes for redshift resolves
two of the preeminent mysteries in cosmology: first, dark energy is not
supported by observations of Type Ia supernovae and second, the Hubble tension
is due to the errors in the K-correction equation.
\end{abstract}

@@

The effect of using an incorrect redshift correction for SnIa is that we think
objects are farther away than they really are; this effect compounds for
greater distances. Up until \citet{riess1998}, we did not have distant enough
observations for this error to matter much for cosmological models, but by the
late 1990s, it became clear that our measurements for distance and redshift
were not linear. This realization led to a model that utilized a cosmological
constant $\Lambda$ and dark energy in order to explain the non-linear
distance-redshift graph. We will show in Section \ref{sec:conclusions} that
correcting the flaws with K-correction leads to a linear graph that does not
need to rely on a cosmological constant.

@@

Observational data from SnIa are essential for the calibration of models that
use redshift to estimate distance. The approximately linear relationship
between redshift and luminosity distance, often called the Hubble-Lema\^{i}tre law,
describes how quickly the universe is expanding. However, \citet{riess1998}
and \citet{perlmutter1999} presented evidence that there is not a linear
relationship between redshift and distance, but instead, distant objects are
farther away than their redshift would predict (see Figure
\ref{fig:mu_distance_vs_redshift}). This phenomenon implies that the
acceleration of the universe is faster today than it was for old observations.
The cause of this phenomenon was unknown and was referred to as dark energy.

\begin{figure}
  \plotone{lum_distance_vs_redshift.pdf}
  \caption{The relationship between luminosity distance and redshift for two
  treatments of magnitude data. The displayed points are roughly a third of the
  values in the full SnIa dataset published in \citet{abbott2024}, selected
  with uniform redshift spacing to aid visibility. The red $k(z) = 1$ treatment,
  which represents the uncorrected values, is clearly non-linear while the blue
  $k(z) = 1 + z$ treatment, which fixes the K-correction redshift error,
  appears to be linear.}
  \label{fig:mu_distance_vs_redshift}
\end{figure}

@@

\begin{figure}
  \plotone{k_equation_flow.pdf}
  \caption{The value $K'_{xy}$ is equal to the number of photons we want to
  report in the target filter divided by the number of photons we measure in
  the observation filter.  Deriving this value starts with $F(\lambda)$, the
  spectral energy density, which we then convert to $F'(\lambda)$, the photon
  density for the rest frame.  Starting at the top right corner of the figure,
  we show the process of computing $R'(\lambda)$, the photon density in the
  observation frame, in three phases. First we stretch the photon density, but
  this step inflates counts. In the second step, we correct for the inflated
  counts by multiplying by $1/(1+z)$; at this point, the total count equals the
  total count of $F'(\lambda)$. Finally, in the third step we finish
  calculating the observation frame photon density $R'(\lambda)$ by accounting
  for time dilation, which also reduces photon counts by a factor of $1/(1+z)$.
  We can compute the expected ratio of photons by totalling the area under the
  curves in the bottom two panels.
  }
  \label{fig:k-example}
\end{figure}

@@

  In order to account for this spectral bandwidth stretching effect, we
  multiply $F'$ by $1/(1+z)$.

  \item The stretching of space increases the distance between photons while
  they are traveling. To an observer, this phenomenon appears like time
  dilation, although cosmological time dilation is due to a different mechanism
  than relativistic time dilation. This effect reduces the photon arrival rate
  by a factor of $1/(1+z)$.

  In order to account for cosmological time dilation, we multiply $F'$ by a
  second factor of $1/(1+z)$.
\end{itemize}

@@

In order to calculate the amount of flux $\mathcal{F}_x$ measured in filter
$x$, we need to compute the photon density $F'(\lambda)$ and multiply it by
the sensitivity $S_x(\lambda)$, which represents the proportion of photons with
wavelength $\lambda$ that filter $x$ will measure. We then need to sum over
all wavelengths, which is expressed with the equation

@@

@@

\section{Conclusions}
\label{sec:conclusions}

\begin{figure}
  \plotone{velocity_vs_distance.pdf}
  \caption{The relationship between expansion velocity and distance. The slope
  of this graph demonstrates the Hubble constant. The data for these SnIa
  observations comes from the Dark Energy Survey \citep{vincenzi2024}, but the
  magnitudes are corrected to account for time dilation by adding
  $-2.5 log(1 + z)$.
  }
\label{fig:expansion}
\end{figure}
